Station summary

### 2023-02-21 reports/02_stations.qmd
fix zoop station maps (pseudo-log abundance, better gradient)

>>>>

## Zooplankton maps

```{r}
#| label: station_map_fn

station_map <- function(var, pseudolog = FALSE) {
  zoop_trans <- zoop_sf
  if (pseudolog) {
    old_var <- var 
    var <- str_glue("log({var}+1)")
    zoop_trans[[var]] <- log(zoop_trans[[old_var]] + 1)
  }
  ant_basemap(map_lim) +
    geom_sf(aes(color = .data[[var]]), zoop_trans, size = 2, shape = 15) +
    facet_wrap(~ Year) +
    scale_x_continuous(breaks = c(-60, -55)) +
    scale_y_continuous(breaks = c(-63, -62, -61, -60)) +
    { if (is.numeric(zoop_trans[[var]])) 
      scale_color_distiller(palette = "PuRd", direction = 1) } +
    coord_ant(map_lim) +
    theme(legend.position = "bottom")
}

```

```{r}
#| label: zoop_maps

zoop_vars_raw <- c("Winter Cluster factor",
                   "NMDS_x",
                   "NMDS_y",
                   "NMDS_z")
zoop_vars_pseudolog <- c("Amphipoda_Primno_N.A",
                         "Amphipoda_Themisto_N.A",
                         "Chaetognatha_N.A",
                         "Copepoda_Cacutus_N.A",
                         "Copepoda_Cprop_N.A",
                         "Copepoda_Heterorhabdus_N.A",
                         "Copepoda_Metridia_N.A",
                         "Copepoda_Paraeuchaeta_N.A",
                         "Copepoda_Pleuromama_N.A",
                         "Copepoda_Rhincalanus_N.A",
                         "Euphausiidae_Ecrystall_Adult",
                         "Euphausiidae_Efrigida_Adult",
                         "Euphausiidae_Efrigida_Larvae",
                         "Euphausiidae_Esuperba_Adult",
                         "Euphausiidae_Etricantha_Adult",
                         "Euphausiidae_Tmac_Adult",
                         "Euphausiidae_Tmac_Larvae",
                         "Gastropoda_Clione_N.A",
                         "Gastropoda_Limacina_N.A",
                         "Ostracoda_N.A",
                         "Radiolaria_N.A",
                         "Siphonophora_N.A",
                         "Tunicata_Salpa_N.A",
                         "Euphausiidae_Esuperba_F_Tot",
                         "Pisces_Paralepididae_NotolepisSpp_Larvae_Tot",
                         "Pisces_Myctophidae_Adult_Tot",
                         "Pisces_Myctophidae_Larvae_Tot",
                         "Pisces_Other_Larvae_Tot",
                         "Pisces_Chaenichthyidae_Larvae_Tot",
                         "Pisces_Nototheniidae_Larvae_Tot")

walk(zoop_vars_raw, compose(print, station_map))
walk(zoop_vars_pseudolog, 
     compose(print, partial(station_map, pseudolog = TRUE)))

```

## Physics maps

```{r}
#| label: physics_maps

physics_vars <- c("Net.ice.type",
                  "Net.ice.percent",
                  "zuml_m",
                  "avg.Dens.Diff",
                  "avg.salinity",
                  "avg.temp",
                  "Integ.chla.zuml",
                  "Integ.phae.zuml",
                  "Integ.chla.100m",
                  "Integ.phae.100m")

walk(physics_vars, compose(print, station_map))

```
